\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{sectsty}

\geometry{margin=0.5in}
\setlist[itemize]{left=0pt, itemsep=0pt}
\subsubsectionfont{\normalfont}

\begin{document}
\pagestyle{empty}

\begin{center}
  {\LARGE \textbf{Robert Martinez Marenco}} \\
  \vspace{4pt}

  \href{mailto:rdmm404@gmail.com}{rdmm404@gmail.com} |
  \href{https://github.com/rdmm404}{github.com/rdmm404} |
  \href{https://linkedin.com/in/rdmm404}{linkedin.com/in/rdmm404}

  Permanent Resident in Toronto, ON
\end{center}

\hrule
\vspace{4pt}

% Professional Summary
\section*{Summary}
Software Engineer with 3+ years of experience in designing and developing scalable full stack web applications
and cloud-native microservices. Skilled at translating complex business requirements into robust, containerized solutions
for high-demand platforms, using Python, React, TypeScript, and modern CI/CD practices.

% Work Experience
\section*{Work Experience}

\subsubsection*{%
  \textbf{Software Engineer} at \href{https://www.achievers.com/}{Achievers}, Toronto
  \hfill
  \textit{November 2022 - Present}
}
\begin{itemize}
  \item Designed, developed and maintained various containerized Python microservices in a cloud-first architecture with scalability,
    performance and global availability in mind, for a B2B SaaS with millions of users around the world.

  \item As a full stack engineer, enhanced our domain-driven GraphQL gateway in TypeScript and contributed to
    developing React micro-frontends, ensuring seamless integration between backend data and the user interface.

  \item Leveraged extensive Google Cloud Platform (GCP) expertise across diverse tools. This includes GRPC and PubSub for service communication,
    Kubernetes Engine for deploying and scaling services, Artifact Registry for container images and packages,
    Cloud Buckets for file storage and Secrets for storing sensitive information.

  \item Core developer on the marketplace team -- responsible for a platform that processes 10+ orders per minute, and drove \$10M+ revenue in 2024.
    Maintained order processing and vendor integration services with high availability, and resolved order and catalog issues promptly within SLAs.

  \item Contributed significantly to integrating external services, such as Netsuite and Akeneo,
    into our platform to streamline business processes.
    The Akeneo integration improved efficiency in the product merchandising pipeline by 66.6\%.

  \item Developed efficient data operations in microservices by writing and debugging MySQL queries,
    while leveraging Redis as a high-speed cache for requests and responses.
    % \item Maintained a PHP legacy monolithic application and participated in the migration of various functionalities to microservices architecture.
  \item Proposed using a new Python package manager (uv) as a proof of concept to accelerate package installations in our Drone CI/CD
    pipelines, cutting overall build times by over 50\%.
\end{itemize}

\subsubsection*{%
  \textbf{Web Developer} at \href{https://www.tecnoglass.com/en/}{Tecnoglass}, Colombia
  \hfill
  \textit{November 2021 - November 2022}
}
\begin{itemize}
  \item Developed multiple full stack web applications using Python, Django, Bootstrap and jQuery with PostgreSQL as database.
    This was part of the digital transformation initiative to reduce paperwork and optimize various business processes.
  \item Design and implementation of a temperature and humidity monitoring system in glass assembly plants using LoraWAN.
    Led the entire hardware selection, configuration, and installation process, and developed a real-time
    dashboard using Python, Django Channels, Websockets, HTML, JS, and CSS.
  \item Played a major role in containerizing applications and deploying in bare-metal on-premise servers using Docker and Docker Compose.
    % \item Developed a centralized system to handle authentication across multiple web applications with SSO, internally connecting to an
    %   LDAP Active Directory user database, which gets populated whenever a new employee joins the company.
\end{itemize}

% Education
\section*{Education}
\subsubsection*{\textbf{B.Sc. in Electronic Engineering} from Universidad del Norte, Colombia \hfill \textit{Graduated March 2023}}
\begin{itemize}
  \item Graduated cum laude in recognition of the excellence of my final thesis and academic performance.
\end{itemize}

% Skills
\section*{Skills}
\begin{itemize}
  \item \textbf{Languages:} Python, JavaScript, SQL, TypeScript, PHP, HTML, CSS
  \item \textbf{Frameworks:} Flask, FastAPI, Django, React
  \item \textbf{Technologies:} GRPC, PubSub, GraphQL, Docker, Kubernetes, CI/CD, DroneCI, GitHub Actions
  \item \textbf{Cloud Providers:} Google Cloud Platform (GCP), AWS
  \item \textbf{Databases:} MySQL, PostgreSQL, Redis
  \item \textbf{Tools:} Git, Github, VS Code, Postman
\end{itemize}

% TODO: Projects section.
\end{document}
