\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{sectsty}

\geometry{margin=0.65in}
\setlist[itemize]{left=0pt, itemsep=0pt}
\subsubsectionfont{\normalfont}

\begin{document}
\pagestyle{empty}

\begin{center}
  \section*{\LARGE Robert Martinez Marenco}
  \href{mailto:rdmm404@gmail.com}{rdmm404@gmail.com} |
  \href{https://github.com/rdmm404}{github.com/rdmm404} |
  \href{https://linkedin.com/in/rdmm404}{linkedin.com/in/rdmm404}

  Permanent Resident in Toronto, ON
\end{center}

\hrule
\vspace{4pt}

% Professional Summary
\subsection*{Summary}
Software Engineer with 4+ years of experience designing scalable, cloud-native backend microservices.
Skilled at building reliable distributed systems with Python, Go, API design, database optimization,
observability, and CI/CD automation.
% Work Experience
\subsection*{Work Experience}

\subsubsection*{%
  \textbf{Intermediate Software Engineer} at \href{https://www.achievers.com/}{Achievers}, Toronto
  \hfill
  \textit{October 2025 - Present}
}
\begin{itemize}
  \item Design, develop, and maintain cloud-based Python and Go microservices for a global B2B SaaS, using GCP, gRPC, Pub/Sub, and Kubernetes (GKE) for scalable service communication and deployment.
  \item Contributed heavily to design and implementation of a resilient top-up checkout workflow, building Python backend flows, a Go-based Avalara tax integration, Stripe payment handling, and saga-style distributed transaction coordination.
  % Add captured revenue metric once available.
  % Interview details: fallback polling jobs, checkout queue state machine, Pub/Sub redelivery, DLT management,
  % UUID deduplication, simultaneous checkout locks across devices, abort/refund paths.
  % TODO: Consider splitting into design + implementation bullets for payment/platform-focused roles.
  \item Contributed to Elasticsearch indexing pipeline simplification, helping evaluate architecture tradeoffs and implementing Go batch processor workers, queue tuning, and Airflow/Dataflow orchestration changes that reduced cluster CPU by ~30\% and memory pressure by ~20\% while keeping search latency under 200ms.
  % \item Partnered with SRE to optimize Elasticsearch index mappings by removing unused indexed fields, correcting data types,
  %   and preventing unwanted extra fields, reducing UAT cluster memory pressure by 50\%+ ahead of production rollout.
  \item Built internal AI tooling with a RAG pipeline and MCP server for vendor API documentation, retrieval, and JSON config validation, reducing vendor integration timelines from 4 weeks to 3 and helping the team exceed its annual integration goal by 20\% (12/10).
  \item Improved New Relic observability for Elasticsearch data sync queues with custom queue-state events, backlog alerts, and dashboards; implementation pattern was later standardized in the shared batch processing library.
  \item Mentored 2 co-op software engineers through onboarding and project delivery, providing code reviews, pair programming support, and technical guidance across marketplace backend services.
  % Optional AI leadership bullet:
  % \item Contributed marketplace-focused AI skills and checkout triage runbooks to an internal skill marketplace,
  %   and hosted team knowledge-transfer sessions to improve AI-assisted development and production support workflows.
  % TODO: Uncomment once shipped.
  % \item Improved checkout observability by tagging New Relic transactions with order metadata and terminal outcomes,
  %   enabling alerts for abnormal aborted-order rates and dashboards for checkout volume, success, and failure trends.
  % Future/search architecture bullet: Sphinx deprecation project, search architecture tradeoffs,
  % Elasticsearch migration decisions, and implementation impact once shipped/measured.
\end{itemize}

\subsubsection*{%
  \textbf{Software Engineer} at \href{https://www.achievers.com/}{Achievers}, Toronto
  \hfill
  \textit{November 2022 - October 2025}
}
\begin{itemize}
  \item Created reusable GraphQL endpoints with Fastify, Node.js, and TypeScript, serving as a gateway and data aggregation layer between gRPC microservices, legacy REST APIs, and front-end applications.
  \item Utilized Google Cloud Platform (GCP) services including Kubernetes Engine, Artifact Registry, Pub/Sub, gRPC, Cloud Storage Buckets, and Secret Manager for application deployment, communication, and storage.
  \item Maintained highly available order processing and vendor integration services for a marketplace platform handling 10+ orders/min (\$10M+ 2024 revenue), resolving critical production issues within SLAs.
\end{itemize}

\subsubsection*{%
  \textbf{Web Developer} at \href{https://www.tecnoglass.com/en/}{Tecnoglass}, Colombia
  \hfill
  \textit{November 2021 - November 2022}
}
\begin{itemize}
  \item Developed web applications using Python, Django, JavaScript, and PostgreSQL to reduce paperwork and optimize business processes; built a centralized Flask REST API for LDAP-backed authentication.
  \item Designed and implemented a LoRaWAN temperature and humidity monitoring system for glass assembly plants, including hardware selection, installation, and a real-time Django Channels dashboard.
\end{itemize}

% Education
\subsection*{Education}
\subsubsection*{\textbf{B.Sc. in Electronic Engineering} from Universidad del Norte, Colombia \hfill \textit{Graduated March 2023}}
\begin{itemize}
  \item Graduated cum laude in recognition of the excellence of my final thesis and academic performance.
\end{itemize}

% Skills
\subsection*{Skills}
\begin{itemize}
  \item \textbf{Languages:} Python, Go, JavaScript, SQL, TypeScript, PHP, HTML, CSS.
  \item \textbf{Frameworks:} Flask, FastAPI, Django, GraphQL, React.
  \item \textbf{Cloud \& DevOps:} Google Cloud Platform (GCP), AWS, DroneCI, GitHub Actions, Airflow.
  \item \textbf{Technologies:} MySQL, PostgreSQL, MongoDB, Redis, Elasticsearch, gRPC, Pub/Sub, Docker, Kubernetes, New Relic.
\end{itemize}

% TODO: Projects section
\end{document}
