\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{sectsty}

\geometry{margin=0.65in}
\setlist[itemize]{left=0pt, itemsep=0pt}
\subsubsectionfont{\normalfont}

\begin{document}
\pagestyle{empty}

\begin{center}
  \section*{\LARGE Robert Martinez Marenco}
  \href{mailto:rdmm404@gmail.com}{rdmm404@gmail.com} |
  \href{https://github.com/rdmm404}{github.com/rdmm404} |
  \href{https://linkedin.com/in/rdmm404}{linkedin.com/in/rdmm404}

  Permanent Resident in Toronto, ON
\end{center}

\hrule
\vspace{4pt}

% Professional Summary
\subsection*{Summary}
Software Engineer with 3+ years of experience in designing and developing scalable full stack web applications
and cloud-based backend microservices. Skilled at translating complex business requirements into robust, containerized solutions
for high-demand platforms, using Python, React, TypeScript, and modern CI/CD practices. Known for being a quick learner
who rapidly adapts to new projects and technologies. Seeking a challenging role in a fast-paced,
collaborative environment that offers meaningful work and opportunities for continuous growth.
% Work Experience
\subsection*{Work Experience}

\subsubsection*{%
  \textbf{Software Engineer} at \href{https://www.achievers.com/}{Achievers}, Toronto
  \hfill
  \textit{November 2022 - Present}
}
\begin{itemize}
  \item Designed, developed, and maintained cloud-based Python microservices for a global B2B SaaS, utilizing
  Google Cloud services---such as gRPC and PubSub for service communication and Kubernetes (GKE) for scalable deployment.
  \item Created and maintained reausable GraphQL endpoints, using Fastify, Node.js and TypeScript. These served as a gateway and data
  aggregation layer between gRPC microservice endpoints, legacy REST API endpoints and the front-end application.
  \item Implemented new components in our React front-end application ---written in JavaScript---,
  following design guidelines and Figma prototypes provided by the Product and UX Design teams.
  % \item Leveraged extensive Google Cloud Platform (GCP) expertise across diverse tools. This includes GRPC and PubSub for service communication,
  %   Kubernetes Engine for deploying and scaling services, Artifact Registry for container images and packages,
  %   Cloud Buckets for file storage and Secrets for storing sensitive information.

  \item Core developer on the marketplace team---responsible for a platform that processes 10+ orders per minute, and drove over \$10M in
  revenue in 2024. Operated within an Agile Scrum environment and maintained highly available order processing and vendor integration
  services, resolving order and catalog issues promptly within SLAs.

  \item Contributed significantly to integrating external services APIs---such as Netsuite and Akeneo--- into our platform to streamline
  business processes, improving efficiency in the product merchandising pipeline by 66.6\%.

  \item Optimized database operations by migrating expensive MySQL queries to read-only replicas after identifying
  bottlenecks during execution. Increased performance in microservice endpoints by implementing caching layers
  using Redis.
    % \item Maintained a PHP legacy monolithic application and participated in the migration of various functionalities to microservices architecture.
  \item Implemented proof of concept for CI/CD pipeline optimization, by using a new Python package manager. This reduced build
  times by over 50\% and was implemented for all services across the company.
\end{itemize}

\subsubsection*{%
  \textbf{Web Developer} at \href{https://www.tecnoglass.com/en/}{Tecnoglass}, Colombia
  \hfill
  \textit{November 2021 - November 2022}
}
\begin{itemize}
  \item Developed multiple full stack web applications using Python, Django, HTML, CSS, and JavaScript, with PostgreSQL as the database.
    This was part of an initiative to reduce paperwork and optimize business processes.
    \item Developed a centralized RESTf API to handle authentication across multiple web applications, internally connecting to an
    LDAP Active Directory user database, using Flask and Python.
  \item Designed and implemented a temperature and humidity monitoring system in glass assembly plants using LoraWAN.
    Led the entire hardware selection, configuration, and installation process, and developed a real-time
    dashboard using Python, Django Channels, Websockets, HTML, JavaScript, and CSS.
  \item Played a major role in containerizing applications and deploying in bare-metal on-premise servers using Docker and Docker Compose.
\end{itemize}

% Education
\subsection*{Education}
\subsubsection*{\textbf{B.Sc. in Electronic Engineering} from Universidad del Norte, Colombia \hfill \textit{Graduated March 2023}}
\begin{itemize}
  \item Graduated cum laude in recognition of the excellence of my final thesis and academic performance.
\end{itemize}

% Skills
\subsection*{Skills}
\begin{itemize}
  \item \textbf{Languages:} Python, JavaScript, SQL, TypeScript, PHP, HTML, CSS.
  \item \textbf{Frameworks:} React, GraphQL, Flask, FastAPI, Django.
  \item \textbf{Cloud \& DevOps:} Google Cloud Platform (GCP), AWS, DroneCI, GitHub Actions.
  \item \textbf{Technologies:} MySQL, PostgreSQL, Redis, GRPC, PubSub, Docker, Kubernetes.
\end{itemize}

% TODO: Projects section
\end{document}
